---
title: "Exploring Weather Data with ropenwhether"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ropenweather-tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ropenwhether)
```

## Introduction

ropenwhether is an R package designed for fetching, processing, and visualizing weather data from the OpenWeatherMap API. This vignette demonstrates how to use its functionalities effectively.


## Getting Started
Load package:
```{r}
library(ropenwhether)
```

Before using the package, ensure you have an API key from OpenWeatherMap. Store your API key as follows:
```{r}
api_key <- "f4ae84f3cc4c51353a1ae2279dd7a60b" # Replace with your actual API key
```

## Fetching Current Weather
To get current weather information for a specific location:
```{r}
lat <- 40.7128  # Example latitude for New York City
lon <- -74.0060 # Example longitude for New York City
current_weather <- get_current_weather(lat, lon, api_key)
```

## Fetching Weather Forecast
```{r}
forecast_weather <- get_forecast_weather(lat, lon, api_key)
```

# Processing Weather Data
### Current Weather
Process the fetched current weather data:
```{r}
processed_current <- process_current_weather(current_weather)

```

### Weather Forecast
Process the fetched forecast weather data:
```{r}
processed_forecast <- process_forecast_weather(forecast_weather)
```

## Data Visualization
### Visualizing Current Weather
Visualize the current weather conditions:
```{r}
visualize_current_weather(processed_current)
```

### Visualizing Weather Forecast
Create visualizations for the weather forecast:
```{r}
visualize_forecast_weather(processed_forecast)
```

## Conclusion
In this vignette, we explored how to fetch, process, and visualize weather data using the ropenwhether package. The package simplifies the interaction with the OpenWeatherMap API and provides tools for effective data visualization.


